---
title: "Assignment_1 - Moving Averages"
author: "Carlos Araya"
date: "March 18, 2017"
output:
  html_document: default
  pdf_document: default
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

This document was scribed with a use plotly package intention and explain Moving Averages formula

## Moving Averages

In statistics, a moving average (rolling average or running average) is a calculation to analyze data points by creating series of averages of different subsets of the full data set.

### Simple moving average

In financial applications a simple moving average (SMA) is the unweighted mean of the previous n data. However, in science and engineering the mean is normally taken from an equal number of data on either side of a central value.

$$SMA = \frac{1}{n}\sum_{i=0}^{n-1} X_{M-i}$$

### Exponential Moving Average

An exponential moving average (EMA), also known as an exponentially weighted moving average (EWMA), is a type of infinite impulse response filter that applies weighting factors which decrease exponentially.

$$EMA_t = EMA_{t-1} - \alpha \times (X_t - EMA_{t-1}) $$

### A Plot with both

```{r Candlestick, echo=FALSE, message=FALSE, warning=FALSE}

library(plotly)
library(dplyr)
library(quantmod)

prices <- getSymbols("MSFT", auto.assign = F)
prices <- tail(prices, 100) # for the assignmet use only the last 50
dat <- as.data.frame(prices)

dat$date <- index(prices)
names(dat) <- sub("^MSFT\\.", "", names(dat))
# create variable with hovertext displaying values of every variable
vars <- Map(function(x, y) paste0(x, ": ", y), names(dat), dat)
dat$txt <- Reduce(function(x, y) paste0(x, "<br />", y), vars)

for (i in 1:length(dat[,1])) {
  if (dat$Close[i] >= dat$Open[i]) {
    dat$direction[i] = 'Increasing'
  } else {
    dat$direction[i] = 'Decreasing'
  }
}

ema.20 <-   EMA(dat[,"Close"], 20)
sma.20 <-   SMA(dat[,"Close"], 20)
#dema.20 <-  DEMA(ttrc[,"Close"], 20)
#evwma.20 <- EVWMA(ttrc[,"Close"], ttrc[,"Volume"], 20)
#zlema.20 <- ZLEMA(ttrc[,"Close"], 20)
#alma <- ALMA(ttrc[,"Close"])
#hma <- HMA(ttrc[,"Close"])

dat <- subset(cbind(dat, data.frame(ema.20), data.frame(sma.20)), date >= date[20])

## Candlerplot with segments
candlerplot <- plot_ly(dat, x = ~date, xend = ~date, color = ~Close > Open,
                       colors = c("red", "forestgreen"), hoverinfo = "none") %>%
  add_segments(y = ~Low, yend = ~High, size = I(1), legendgroup = "Not") %>%
  add_segments(y = ~Open, yend = ~Close, size = I(3), legendgroup = "Not") %>%
  add_trace(y = ~ema.20 , name = "EMA", type = 'scatter', mode = 'lines'
            , line = list(color = 'blue', width = 0.5)
            , legendgroup = "MA") %>%
  add_trace(y = ~sma.20 , name = "SMA", type = 'scatter', mode = 'lines'
            , line = list(color = 'grey', width = 0.5)
            , legendgroup = "MA") %>%
  layout(showlegend = FALSE)

## Volume BarChar
volume<- plot_ly(dat, x=~date, y=~Volume, type='bar', name = "AAPL Volume",
        color = ~direction, colors = c("red", "forestgreen")) %>%
  layout(yaxis = list(title = "Volume"))


subplot(candlerplot, volume, heights = c(0.7,0.2), nrows=2,
        shareX = TRUE, titleY = TRUE) %>%
  rangeslider()

```

> SMS in grey line and EMA in blue line.

